MCC Predictions

### 2018-06-19 stats/ex3_comparisons.Rmd
updating model predictions

@@

@@

@@

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.prior.regPrior,
  llh.rsa.regPrior %>% filter(value != "-Infinity") %>% mutate(value = as.numeric(value)),
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

@@

llh.plot <- likelihood_overview %>%
  group_by(Model)%>%
  summarize(logSumExp = logSumExp(value),
            max = max(value))%>%
  mutate(Model = reorder(Model,logSumExp))

ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))

>>>>

```{r model prior2 loglikelihood}
prior.loglikelihood2 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: two_objects, ps: conditionSpecificPriors[0].priorProbs}));
      return obj.shape == "circle" ? 1 : 0
    }})

@@

```{r model prior noise loglikelihood}
prior.noise.loglikelihood2 <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: two_objects, ps: conditionSpecificPriors[0].priorProbs}));
      return obj.shape == "circle" ? 1 : 0
    }})

@@

llh.prior2 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood2, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs2), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only - non normalized")

@@

llh.prior.noise2 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood2, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs2), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Noisy - non normalized")

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.prior2,
  llh.rsa.noise,
  llh.prior.noise,
  llh.prior.noise2,
  llh.prior.regPrior,
  llh.rsa.regPrior %>% filter(value != "-Infinity") %>% mutate(value = as.numeric(value)),
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

@@

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

llh.plot <- likelihood_overview %>%
  group_by(Model)%>%
  summarize(logP = max(value))%>%
  mutate(Model = reorder(Model,logP))

ggplot(llh.plot, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)
